\LARGE \bf\vspace{-10mm} Face Recognition: Too Bias, or Not Too Bias?

### 2020-02-12 sections/analysis.tex
final changes for arxiv

\begin{figure}[t!]
	\centering    
	\includegraphics[width=\linewidth]{images/confusion.pdf}
		\caption{\small{\textbf{Confusion matrix.} Percent error (Rank 1) for all faces of \gls{bfw} queried against all others. Notice errors concentrate within a subgroup, consistent with the \gls{sdm} in Fig.~\ref{fig:detection-model} (\ie \gls{af} show worst performance, and is mostly confused with faces of the same demographic). This plot is evidence that while race/ethnicity may be challenging to define, the subgroups are meaningful.}}
		\label{fig:confusion} 
		\vspace{-5mm}
\end{figure}

@@

\begin{figure}[t!] 
	\centering    
	\includegraphics[width=\linewidth] {images/human_eval.pdf}
		\caption{\small{\textbf{Qualitative results of human assessment.} $\checkmark$ for \emph{match}; $\times$ for \emph{non-match}, which scores plotted next to each. Humans tend to be more successful at recognizing their own subgroup, with few exceptions (bottom). }}
		% (\eg bottom row). } Result summary in Table~\ref{tab:human-eval}.
		\label{fig:human-eval} 
		\vspace{-5mm}
\end{figure} 
\vspace{-2mm}
% \vspace{-5pt}
\subsection{Human evaluation}
 Quantitative and qualitative results are in Table~\ref{tab:humsn-eval-results} and Fig.~\ref{fig:human-eval}, respectfully. One might expect that the most exposure to others would be within the same subgroup, and, therefore, would be best at labeling their own. Secondarily, they would be best at labeling images of the same ethnicity, but opposite gender. Our findings concur. Each subgroup is best at labeling their type, and then second best at labeling the same ethnicity but opposite sex. Interestingly, each group of images is best tagged by the corresponding subgroup, with the second-to-best having the same ethnicity and opposite gender. On average, subgroups are comparable at labeling images.

>>>>

\begin{figure}[t!]
	\centering    
	\includegraphics[width=\linewidth]{figures/confusion.pdf}
		\caption{\small{\textbf{Confusion matrix.} Percent error (Rank 1) for all faces of \gls{bfw} queried against all others. Notice errors concentrate within a subgroup, consistent with the \gls{sdm} in Fig.~\ref{fig:detection-model} (\ie \gls{af} show worst performance, and is mostly confused with faces of the same demographic). This plot is evidence that while race/ethnicity may be challenging to define, the subgroups are meaningful.}}
		\label{fig:confusion} 
		\vspace{-5mm}
\end{figure}

@@

\begin{figure}[t!] 
	\centering    
	\includegraphics[width=\linewidth] {figures/human_eval.pdf}
		\caption{\small{\textbf{Qualitative results of human assessment.} $\checkmark$ for \emph{match}; $\times$ for \emph{non-match}. Accuracy scores shown as bar plots. Humans are most successful at recognizing their own subgroup, with a few exceptions (\eg bottom).}}
		% (\eg bottom row). } Result summary in Table~\ref{tab:human-eval}.
		\label{fig:human-eval} 
		\vspace{-5mm}
\end{figure} 
\vspace{-2mm}
% \vspace{-5pt}
\subsection{Human evaluation}
 Quantitative and qualitative results are in Table~\ref{tab:humsn-eval-results} and Fig.~\ref{fig:human-eval}, respectfully. One might expect that the most exposure to others would be within the same subgroup, and, therefore, would be best at labeling their own. Secondarily, they would be best at labeling images of the same ethnicity, but opposite gender. Our findings concur. Each subgroup is best at labeling their type, and then second best at labeling the same ethnicity but opposite sex. Interestingly, each group of images is best tagged by the corresponding subgroup, with the second-to-best having the same ethnicity and opposite gender. On average, subgroups are comparable at labeling images.

### 2020-02-12 sections/introduction.tex
final changes for arxiv

\begin{figure}[t!]
\centering
         \includegraphics[trim=0in 0.2in 0in 0in,clip,width=.9\linewidth]{images/montage.pdf}  
\caption{\textbf{\gls{bfw}.} The average face of its different subsets: \emph{top-left}: the entire \gls{bfw}; \emph{top-row} per race;  \emph{left-column}: per gender. The others represent the ethnicity and gender of the race and gender, respectfully. Table~\ref{tab:ethnic-splits} defines the acronyms of subgroups.}
\label{fig:avg-faces}
% \vspace{-3pt}
\end{figure}

@@

\begin{table*}[!t]
    \centering
    \caption{\small{\textbf{Database stats and nomenclature, optimal thresholds ($t_o$), and accuracy scores.} \textit{Header:} Subgroup definitions. \textit{Top-row:} Statistics of \gls{bfw}. \textit{Middle-row:} Number of pairs for each partition. \textit{Bottom-row:} Accuracy when applying a global threshold $t_g$, the optimal threshold $t_o$, and accuracy with $t_o$ per subgroup. Columns grouped by race and then further split by gender. Out of millions of pairs, accuracy is inconsistent across subgroups. Furthermore, $F$ tend to perform inferior to that of $M$ (\ie up to 8\%).}}\label{tab:ethnic-splits}
    \scalebox{1}{
     \resizebox{\textwidth}{!}{%
    \begin{tabular}{r c c c c c c c c l}
        \toprule
        & \multicolumn{2}{c}{Asian (A)} & \multicolumn{2}{c}{Black (B)}  & \multicolumn{2}{c}{Indian (I)}& \multicolumn{2}{c}{White (W)}\\
        \cmidrule(l){2-3} \cmidrule(l){4-5} \cmidrule(l){6-7}\cmidrule(l){8-9} % spanning less than the full width of the table - you can add (r) or (l) just before the opening curly bracket to shorten the rule on the left or right side
         & Female (AF) & Male (AM) & BF & BM& IF & IM & WF & WM&Aggregated\\ % Column names row
        \midrule

@@

        \# Pairs (Total) & 115,135 & 115,232    &115016 &115,141 & 115287  & 115,152  &  115,223& 115193 & 921,379\\ % row 3
        % \midrule
        \specialrule{.01em}{.05em}{.05em}
        Acc$@t_g$ & 0.876 & 0.944  &0.934 &0.942 &0.922&0.949 &0.916  &0.918&0.925$\pm$0.022 \\
        $t_o$ & 0.235 &  0.274 & 0.267&0.254  &0.299 & 0.295& 0.242 &0.222&0.261\\ % row 4
        Acc$@t_o$ & 0.916 &0.964 &0.955 &0.971 &0.933 &0.958 & 0.969 &0.973 & 0.955 $\pm$ 0.018\\
        \bottomrule
    \end{tabular}}
    \glsunset{af}
    }
    \glsunset{af}
    \glsunset{am}
    \glsunset{bf}
    \glsunset{bm}
    \glsunset{if}
    \glsunset{im}
    \glsunset{wf}
    \glsunset{wm}
    \vspace{-12pt}
\end{table*}

>>>>

\begin{figure}[t!]
\centering
         \includegraphics[trim=0in 0.2in 0in 0in,clip,width=.9\linewidth]{figures/montage.pdf}
\caption{\textbf{\gls{bfw}.} The average face of its different subsets: \emph{top-left}: the entire \gls{bfw}; \emph{top-row} per race;  \emph{left-column}: per gender. The others represent the ethnicity and gender of the race and gender, respectfully. Table~\ref{tab:ethnic-splits} defines the acronyms of subgroups.}
\label{fig:avg-faces}
% \vspace{-3pt}
\end{figure}

@@

\begin{table*}[!t]
    \centering
    \caption{\small{\textbf{Database stats and nomenclature, optimal thresholds ($t_o$), and accuracy scores.} \textit{Header:} Subgroup definitions. \textit{Top-row:} Statistics of \gls{bfw}. \textit{Middle:} Number of pairs for each partition. \textit{Bottom:} Accuracy with a global threshold $t_g$, the optimal threshold $t_o$, and accuracy with $t_o$ per subgroup. Specifically, $t_g$=0.259$\pm$0.002 when averaged across the five folds. Columns grouped by race and then further split by gender. Out of millions of pairs, accuracy is inconsistent across subgroups. Furthermore, $F$ tend to perform inferior to that of $M$ for all but B.}}\label{tab:ethnic-splits}
    \scalebox{1}{
     \resizebox{\textwidth}{!}{%
    \begin{tabular}{r c c c c c c c c l}
        \toprule
        & \multicolumn{2}{c}{Asian (A)} & \multicolumn{2}{c}{Black (B)}  & \multicolumn{2}{c}{Indian (I)}& \multicolumn{2}{c}{White (W)}\\
        \cmidrule(l){2-3} \cmidrule(l){4-5} \cmidrule(l){6-7}\cmidrule(l){8-9} % spanning less than the full width of the table - you can add (r) or (l) just before the opening curly bracket to shorten the rule on the left or right side
         & Female (AF) & Male (AM) & BF & BM& IF & IM & WF & WM&Aggregated\\ % Column names row
        \midrule

@@

        \# Pairs (Total) & 115,135 & 115,232    &115016 &115,141 & 115287  & 115,152  &  115,223& 115193 & 921,379\\ % row 3
        % \midrule
        \specialrule{.01em}{.05em}{.05em}
        Acc$@t_g$ & 0.941 & 0.952  & 0.967 & 0.960 & 0.958 &0.962  & 0.973 & 0.981 &0.962 $\pm$0.012 \\
        $t_o$ & 0.255 &  0.246 & 0.277 &0.242  &0.297 & 0.264& 0.233 &0.239 &0.257$\pm$0.006\\ % row 4

        Acc$@t_o$ & 0.942 &0.952 &0.968 &0.961 &0.960 &0.962 & 0.974 &0.982 & 0.963 $\pm$ 0.012\\
        \bottomrule
    \end{tabular}}
    \glsunset{af}
    }
    \glsunset{af}
    \glsunset{am}
    \glsunset{bf}
    \glsunset{bm}
    \glsunset{if}
    \glsunset{im}
    \glsunset{wf}
    \glsunset{wm}
    \vspace{-12pt}
\end{table*}
